NSync: Boy bands meet nitrogen

### 2020-05-28 manuscript/manuscript.Rmd
updated reference in manuscript.Rmd

Bibliography
============
@article{kellogg2010geospatial,
  title={A geospatial approach for assessing denitrification sinks within lower-order catchments},
  author={Kellogg, DQ and Gold, Arthur J and Cox, Suzanne and Addy, Kelly and August, Peter V},
  journal={Ecological Engineering},
  volume={36},
  number={11},
  pages={1596--1606},
  year={2010},
  publisher={Elsevier}
}

>>>>

Bibliography
============
